PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-06-29 manuscript.natcomm.tex
Add acknowledgement to ChatGPT and use numerics for citaitons.
Fixed minor formatting issues.

% Include natbib
\usepackage{natbib}
%% \setcitestyle{authoryear,round}    % Use authoryear format

@@

Earlier versions utilizing YOLO and U-Net models were built and tested by P.L and C.H.Y.  The experiments were designed by C.W with inputs from J.B.T and C.H.Y.  C.W implemented the residual attention U-Net, prepared the datasets, labeled experimental data, and trained and evaluated the refined neural network model.  The manuscript was written by C.W and C.H.Y with input from all authors.  This material is based upon work supported by the U.S.  Department of Energy, Office of Science, Office of Basic Energy Sciences under Award Number FWP-100643.  Use of the Linac Coherent Light Source (LCLS), SLAC National Accelerator Laboratory, is supported by the U.S.  Department of Energy, Office of Science, Office of Basic Energy Sciences under Contract No.  DE-AC02-76SF00515.

>>>>

% Include natbib
\usepackage{natbib}
\setcitestyle{numbers,square}
%% \setcitestyle{authoryear,round}    % Use authoryear format

@@

Earlier versions utilizing YOLO and U-Net models were built and tested by P.L and C.H.Y.  The experiments were designed by C.W with inputs from J.B.T and C.H.Y.  C.W implemented the residual attention U-Net, prepared the datasets, labeled experimental data, and trained and evaluated the refined neural network model.  The manuscript was written by C.W and C.H.Y with input from all authors.  This material is based upon work supported by the U.S.  Department of Energy, Office of Science, Office of Basic Energy Sciences under Award Number FWP-100643.  Use of the Linac Coherent Light Source (LCLS), SLAC National Accelerator Laboratory, is supported by the U.S.  Department of Energy, Office of Science, Office of Basic Energy Sciences under Contract No.DE-AC02-76SF00515.  C.W acknowledges the assistance provided by ChatGPT from OpenAI in refining the language and enhancing the readability of this paper.
